\begin{thebibliography}{9}

\bibitem{xmile}
  Adler, Steve. \textit{XMILE: System Dynamics Standard @ OASIS}. July 2013.   \url{https://www.ibm.com/developerworks/community/blogs/adler/entry/xmile_system_dynamics_standard_oasis?lang=en}

\bibitem{devs76}
  Zeigler, B. P. \textit{Theory of Modeling and Simulation}. John Wiley, 1976.

\bibitem{devsml}
  Mittal, S., J.L. Risco-Martín and B.P. Zeigler. \textit{DEVSML: automating DEVS execution over SOA towards transparent simulators.}. In M.J. Ades (ed.), Spring Simulation Multiconference, SpringSim 2007, Norfolk, VA, pp. 287-295

\bibitem{qss}
 F. Cellier, E. Kofman. \textit{Continuous System Simulation}. Springer, New York, 2006.

\bibitem{merten1987}
    Merten, P. P., Löffler, R., \& Wiedmann, K. P. \textit{Portfolio simulation: a tool to support strategic management}. System Dynamics Review, 3(2), 81-101. 1987.

\bibitem{xu}
Honggang, Xu, Ali N. Mashayekhi, and Khalid Saeed. \textit{Effectiveness of infrastructure service delivery through earmarking: the case of highway construction in China.} System Dynamics Review 14.2, 223-258. 1998.

\bibitem{ford1998}
Taylor, Tim, and David N. Ford. \textit{Tipping point failure and robustness in single development projects.} System Dynamics Review 22.1, 51-71. 2006.

\bibitem{sterman2001}
    Sterman, John D. \textit{System dynamics modeling: tools for learning in a complex world.} California management review 43.4, 8-25. 2001.
    
\bibitem{xml}
XML. \url{http://www.w3.org/XML/}

\bibitem{pysd}
PySD: Simulating System Dynamics Models in Python. \url{http://pysd.readthedocs.io/en/master/}

\bibitem{muparser}
muparser: Fast Math Parser Library. \url{http://beltoforion.de/article.php?a=muparser}
    
\end{thebibliography}
